---
title: "Homework 1"
author: "Stephanie Gluck"
date: "January 28, 2020"
output: 
  html_document: 
    theme: cerulean
---

```{r setup, include=FALSE}

library(devtools)
dev_mode(T)

library(rio)
library(here)
#library(tidyverse)
library(dplyr)
library(forcats)
#library("ggplot2", lib.loc="~/R-dev")
library(ggplot2,  lib.loc="~/R-dev")

theme_set(theme_minimal(base_size = 12))

knitr::opts_chunk$set(echo = TRUE)
```

## Read in data 

```{r load data}

pth <- here("data")

myfiles = list.files(path=pth, pattern="*.csv", full.names=T)
myfiles

data_csv = lapply(myfiles, readr::read_csv)

assessments <- plyr::ldply (data_csv[1], data.frame)
courses <- plyr::ldply (data_csv[2], data.frame)
studentAssessment <- plyr::ldply (data_csv[3], data.frame)
studentInfo <- plyr::ldply (data_csv[4], data.frame)
studentRegistration <- plyr::ldply (data_csv[5], data.frame)
studentVle <- plyr::ldply (data_csv[6], data.frame)
vle <- plyr::ldply (data_csv[7], data.frame)

rm(data_csv)

```

## Joining and data display 

### Average Final Score in relation to Index of Multiple Depravation and Level of Education 

Intersting to note that if you examine the number of students in each education level, there are only 8 students who reported no formal qualification and 14 students who reported post graduate qualificaiton so those two groups are much smaller relative to the remaining three educaiton groups. 


```{r data_display1, fig.width = 8, fig.height = 6}

d1 <- left_join(studentInfo, studentAssessment)

d1 <- left_join(d1, assessments) %>%
  filter(assessment_type == "Exam") %>%  
  na.omit()

head(d1)

#Box plot 
ggplot(d1, aes(imd_band, score)) +
  geom_boxplot(fill = "seagreen4") +
  coord_flip() + 
  facet_wrap(~highest_education, 3,2) +
  labs(x = "Index of Multiple Depravation Band",
       y = "Average Final Exam Score",
       title = "Average Final Score in Relation to Index of Multiple Depravation",
       subtitle = "Results displayed by Level of Education", 
       caption = "") +
  theme(plot.title.position = "plot")

d1 %>% group_by(highest_education) %>% summarize(n = n())

```

### Engagement of Pass & Distinction students with the VLE materials in relation to their TMA score 

```{r data_display2, fig.width = 9, fig.height = 7}

tma_key <- assessments %>% 
  filter(assessment_type == "TMA") %>% 
  select(-date, -weight)

d2 <- semi_join(studentAssessment, tma_key)

d2 <- left_join(d2, studentInfo) %>% 
  filter(final_result == "Pass" | final_result == "Distinction")

d2 <- left_join(d2, studentVle)

d2 <- d2 %>% 
  group_by(code_module, id_student, final_result) %>%
  summarise(click_m = mean(sum_click),score_m = mean(score, na.rm = T)) %>%
  na.omit()

head(d2)

#Scatter plot
ggplot(d2, aes(click_m, score_m)) +
  geom_point(aes(color = factor(final_result)), size = 2, alpha = 0.4) +
  geom_smooth(method = lm, col = "#fb9a99", size = 1.5) +
  facet_wrap(~code_module, 4, 2) +
  scale_color_brewer("Final Result", 
                     palette = "Paired") +
  labs(x = "Average Number of Interactions with Material",
       y = "Average TMA Score",
       title = "Student Engagement with the VLE materials",
       subtitle = "Results displayed by Average TMA Score, Final Result and Course Modules", 
       caption = "") +
  theme(plot.title.position = "plot", 
        legend.position = c(0.8, 0.1))

```

## Distribution of student TMA score by course modules and gender

```{r data_display3, fig.width = 8, fig.height = 9}

d3 <- left_join(studentInfo, studentAssessment)

d3 <- left_join(d3, assessments)

d3 <- d3 %>% filter(final_result != "Withdrawal", assessment_type == "TMA") %>% group_by(code_module, id_student, gender, assessment_type) %>% summarize(score_m = mean(score)) %>% na.omit()

#Sina plot 
ggplot(d3, aes(code_module, score_m, color = gender)) +
  ggforce::geom_sina() +
  scale_color_brewer("Gender", 
                    palette = "Set1") +
  theme(legend.direction = "horizontal", 
        legend.position = "bottom", 
        legend.key.size = unit(1, "in")) + 
  guides(colour = guide_legend(override.aes = list(size=5))) + 
  stat_summary(fun.data=mean_sdl, 
               fun.args = list(mult=1), 
               geom="errorbar", 
               color="gray20", 
               width=0.2, 
               size = 1,
               position = position_dodge(1), 
               aes(group = gender)) +
  stat_summary(fun.y=mean, 
               geom="point", 
               color="gray20",
               size = 3,
               position = position_dodge(1), 
               aes(group = gender)) +
  labs(x = "Course Modules",
       y = "Average TMA Score",
       title = "Student TMA Score by Course Module and Gender", 
       subtitle = "Results include students who recieved Final Result Designation of Distinction, Pass and Fail") +
  theme(plot.title.position = "plot")

```


## Reproduce figure

```{r reproduce_fig, fig.width = 7, fig.height = 9}

#Data wrangling to reproduce figure 

figure_d <- left_join(studentInfo, studentAssessment)

figure_d <- left_join(figure_d, assessments) %>%
  filter(assessment_type == "TMA")

head(figure_d)

figure_d <- figure_d %>% mutate(final_result = as.factor(final_result),
                  gender = as.factor(gender)) %>% 
  group_by(final_result, highest_education, gender) %>% 
  na.omit() %>% 
  summarize(score = mean(score)) %>% 
  mutate(facet = factor(final_result, levels = c("Fail", "Withdrawn", "Pass", "Distinction")),
         education = factor(highest_education, levels = c("Post Graduate Qualification", 
                                                          "HE Qualification", 
                                                          "A Level or Equivalent", 
                                                          "Lower Than A Level", 
                                                          "No Formal quals")))

ggplot2::ggplot(figure_d, aes(fct_rev(education), score)) +
  geom_line(aes(group = education), color = "gray50", size = 2) +
  geom_point(aes(color = gender), size = 3) +
  facet_wrap( ~ facet, ncol=1) +
  coord_flip() + 
  scale_color_brewer("Gender", 
                    palette = "Set1") +
  labs(x = "Highest Education",
       y = "Average Score",
       title = "Average TMA Scores",
       subtitle = "Results displayed by Education, Gender and Final Result Designation", 
       caption = "Data from Kuzilek, Hlosta & Zdrahal (2017).
       https://analyse.kmi.open.ac.uk/open_dataset") +
  theme(plot.title.position = "plot")

```


